\documentclass[11pt,a4paper]{article}
\usepackage{fullpage}
%%\usepackage{courier}
\usepackage{graphicx}
\usepackage{indentfirst}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{document}

\textbf{Prepare}

\noindent
\hrulefill

\vspace{3mm}

\textbf{gau\_prmtop2gaucom.py} (former amboniom.py)

\noindent
Convert Amber topology to ONIOM model.

\vspace{3mm}

\textbf{gau\_freezecom.py} (former gfreezer.py)

\noindent
Freeze complete residues beyond specified distance.

\vspace{3mm}

\textbf{gau\_setscan.py} (former gscan.py)

\noindent
Specify target distance (or number of steps) of a scan.


\vspace{9mm}

\textbf{Analysis}

\noindent
\hrulefill

\vspace{3mm}

\textbf{gau\_makepdb.py} (former g2pdb.py)

\noindent
Make a .pdb file from .log or .com.

\vspace{3mm}

\textbf{gau\_plot2dscan.py} (former gsurf.py)

\noindent
Plot energy as a function of 2 coordinates in 3D space.

\vspace{3mm}

\textbf{gau\_checklog.py} (former hiig.py)

\noindent
Check energies and convergence status.

\vspace{3mm}

\textbf{gau\_energies.py} (former g09out\_analysis.py)

\noindent
Print energies to .csv file for analysis in spreadsheet.

\vspace{3mm}

\textbf{gau\_measure.py}

\noindent
Measure distance, angle or dihedral.

\vspace{9mm}

\textbf{Restart}

\noindent
\hrulefill

\vspace{3mm}

\textbf{gau\_autorestart.py} (former paimei.py)

\noindent
Automatically restart calculations on linux cluster. Specially useful for
microiterations and internal coordinates errors.

\vspace{3mm}

\textbf{gau\_log2com.py} (former gx.py)

\noindent
Make a new .com file from any opt/scan point from a .log file.

\vspace{9mm}

\textbf{Miscellaneous}

\noindent
\hrulefill

\vspace{3mm}

\textbf{gau\_add\_line.py} 

\noindent
Resolve Gaussview problem in reading all .log lines as ModRed.


\end{document}
